---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Cat Seitz"
date: "02/13/2023"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(dsbox)
library(mosaicData) 
library(ggbreak) 
library(patchwork)
```

### Exercise 1

The original visualization is quite misleading. At first glance, they are trying to make it seem like wearing masks decreases the number of COVID cases. However, there are several problems with their plot. 1) There are 2 y-axes that aren't labeled, so we can't really tell which one is the average daily cases. They make it seem like the mask counties correspond to the left axis and the no-mask counties correspond to the right axis, but it's not super clear and that seems weird because the y-axes aren't that different. 2) Also, the x-axis is only 15-ish days worth of data, so the graph creator could've chosen a time frame that displayed that wearing masks is better for not contracting COVID.

```{r create-dataframe}

mask<- tribble(
  ~date, ~count, ~mask_status,
  "7/12/2020", 25.5, "mask",
  "7/13/2020", 19.8, "mask",
  "7/14/2020", 19.7, "mask",
  "7/15/2020", 20.5, "mask",
  "7/16/2020", 19.9, "mask",
  "7/17/2020", 19.9, "mask",
  "7/18/2020", 20.5, "mask",
  "7/19/2020", 20.0, "mask",
  "7/20/2020", 20.7, "mask",
  "7/21/2020", 21.5, "mask",
  "7/22/2020", 19.9, "mask",
  "7/23/2020", 20.0, "mask",
  "7/24/2020", 20.4, "mask",
  "7/25/2020", 19.0, "mask",
  "7/26/2020", 19.7, "mask",
  "7/27/2020", 17.0, "mask",
  "7/28/2020", 16.1, "mask",
  "7/29/2020", 16.3, "mask",
  "7/30/2020", 16.5, "mask",
  "7/31/2020", 16.0, "mask",
  "8/01/2020", 16.2, "mask",
  "8/02/2020", 15.9, "mask",
  "8/03/2020", 16.0, "mask",
  "7/12/2020", 9.8, "nomask",
  "7/13/2020", 9.1, "nomask",
  "7/14/2020", 9.3, "nomask",
  "7/15/2020", 9.8, "nomask",
  "7/16/2020", 9.9, "nomask",
  "7/17/2020", 9.5, "nomask",
  "7/18/2020", 9.5, "nomask",
  "7/19/2020", 9.1, "nomask",
  "7/20/2020", 8.6, "nomask",
  "7/21/2020", 8.6, "nomask",
  "7/22/2020", 8.8, "nomask",
  "7/23/2020", 8.6, "nomask",
  "7/24/2020", 9.9, "nomask",
  "7/25/2020", 9.9, "nomask",
  "7/26/2020", 10.1, "nomask",
  "7/27/2020", 9.5, "nomask",
  "7/28/2020", 9.5, "nomask",
  "7/29/2020", 9.5, "nomask",
  "7/30/2020", 10.0, "nomask",
  "7/31/2020", 8.9, "nomask",
  "8/01/2020", 9.1, "nomask",
  "8/02/2020", 8.9, "nomask",
  "8/03/2020", 9.1, "nomask",
)

```

### Exercise 2

```{r make-visualization}

xlabels <- sort(unique(mask$date))
xlabels[seq(2, length(xlabels), 2)] <- ""

mask %>%
  ggplot(aes(x = date,
             y = count,
             group = mask_status,
             color = mask_status)) +
  geom_line()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  coord_cartesian(ylim = c(0,25))+
  labs(title = "Kansas COVID-19 7-Day Rolling Average of Daily Cases/Per 100K Population",
       subtitle = "Mask Mandate Counties Vs. No-Mask Mandate Counties",
       x="Date",
       y="Average Daily Cases",
       caption = "Source: Kansas Department of Health and Environment")+
  guides(color=guide_legend(title = "Mask Status"))+
  scale_x_discrete(labels=xlabels)

```


### Exercise 3

In my visualization, the distinction between mask mandate counties and no-mask mandate counties is much more clear, especially with regards to the average daily cases in each place. Now, we can clearly see that no-mask mandate counties have much fewer cases than mask mandate counties, which is opposite to what the original visualization was trying to show. In addition, I made the x-axis display every-other date to make it less cluttered. 

### Exercise 4

This data, which is only 22 days worth of data, shows that counties where there is not a mask mandate have around 10 COVID cases daily and counties with a mask mandate have around 20 COVID cases daily. While this may seem like masks are worse for contracting COVID, there could be a different reason the data look like this. For example, it's likely that counties that enforced a mask mandate were ones that had higher daily cases than counties that didn't enforce a mask mandate. 





